Spec2Fab: A High-Fidelity Mapping from Specification to Fabrication

### 2012-08-01 paper.tex
add built-in component section

\usepackage{caption}
\usepackage{subcaption}
\usepackage[english]{babel}
\title{Goes Here}

@@

We will also use faster resonating actuators and high-speed
camera systems to track material deformations at high frame rates. Furthermore, we plan to track
the whole material volume rather than the outer material surface. This is possible since we can
print materials in clear color as well. Thus small color-coded markers can be easily embedded into
the material structure. These markers can be tracked in 3D using a multi-camera system.
\section{System Description}
The software framework (shown in Figure~\ref{fig:framework}) is composed of 
a set of software
modules that can be easily modified or exchanged. The first component
of this framework is an output-device-independent description API
that allows the user to specify any physical object in terms of its physical
properties such as geometry, mechanical behaviors, and appearance. 
The framework will also provide physically-based
simulation tools that accurately predict the behavior of our output device.
The goal of the optimization module is to search through
the space of possible device outputs and deliver one that best matches the
desired model. In order to evaluate the quality of the match between the
simulation output and the desired model we need to develop appropriate
comparison metrics. Finally, a central component of our framework is
a reduction model which makes the optimization problem tractable by
reducing the search space as much as possible.
The reduction model can specified by experts or deduced from a
set of examples. Next, we will describe each element of the framework in
more detail.
\begin{figure}
\includegraphics[width=0.45\textwidth]{figure/framework.pdf}
\caption{API overview}
\label{fig:framework}
\end{figure}
\subsection{Input API}
Our input API handles three tasks: specifying an optimization problem,
maintaining a material library and configuring existing modules of
the optimization process.
An overview of the three components of our API is shown in Figure~\ref{fig:inputAPI}

\begin{figure}
\includegraphics[width=0.45\textwidth]{figure/inputAPI.pdf}
\caption{Input API overview}
\label{fig:inputAPI}
\end{figure}

Our input API allows a designer to either
define material properties for sections of an object
or specify behavior of an object.
The designer
can use functions to describe properties such as reflectance (e.g., BRDFs, BSSRDFs), 
stiffness, or other spatially varying properties. 
Although it is possible to define the object directly by only specifying material
properties, intuitive user
interfaces will aid in specifying the objects and their properties
in terms of intuitive metaphors.
For example, the elastic properties of an object can be specified by a set of
example displacements from the rest pose and the corresponding applied forces.
\subsection{Search Space Decomposition and Reduction}
Our framework includes an optimization component that
searches through the space of possible device inputs
to find the one that best reproduces
the desired object. Unfortunately, this search space
is usually intractable. For example, when the printing
volume has N voxels and each of these voxels can be
assigned to one of M base materials, the search space
contains $N^M$ choices. To overcome this problem, we decompose the search
space into similar subproblems and also reduce
the search space to a lower-dimensional space using
a reduction model. The goal of the reduction step is to
shrink the search space as much as possible but at the
same time not to prune out good solutions. The low-dimensional space produced by the
reducer can be defined in two different ways. First, a reduction model can be explicitly specified by an expert, for
example, by defining structures of base materials and rules how different base materials can be combined together.
In this paper, all reduction models are manually specified by us.
The second way to specify a reduction model is implicit. In this case, the user provides a set of examples of
valid material structures. Then, a machine learning algorithm infers both basic material structures and the rules
for combining them. The optimization framework can be further improved by employing techniques that cluster
partial solutions that yield similar output properties, avoiding combinatorial explosion of the search space.
Furthermore, we can employ bounds on the solution based on physical constraints of the base materials.
\subsection{Optimization}
Our optimization component is an interface to
existing standard optimization techniques
such as simulated annealing, variational inference and
Markov Chain Monte Carlo methods,
as well as custom optimization algorithms implemented
by more advanced users.
\subsection{Simulation}
Another key step in the process of converting abstractions to physical output is being able to
simulate what an output device is going to generate given a well-defined input. 
A simulation allows the user to preview how the output will look and behave. 
This simulation is a generalization of the print-preview function
available in word processing applications.
As physical output generation might be costly or time-consuming, 
it is extremely beneficial for users to be able to preview the output and make immediate changes to the design.
That means that the simulation must accurately predict the output. 
It's necessary to develop very efficient and accurate rendering
and finite element simulation packages. Since we run the simulation multiple times within the optimization method
we can cache and reuse partial simulation results, speeding up the evaluation process at least 10-100 times.
Furthermore, we will ensure that the simulation is accurate by measuring properties of the printing materials and using
these measurements to estimate the parameters of data-driven material models (e.g., for elasticity, reflectance).
\section{Programming with Our API}
We provide a built-in library that handles common tasks such as assigning texture,
simulating deformation, and optimizing for a stacking.
A casual user mostly make function calls to an existing 
manager to pass data and to run the optimization.
More advanced user can configure the manager to achieve more specific requirements.
For example, he can swap out an existing optimization module to achieve a better accuracy or 
a faster speed.
A professional user can implement more modules when he wants to deal with new
material properties that are not handled by our built-in library. In that case,
he needs to know what value the new property is in print materials, he needs to know
how to simulate for the new property, and how to measure error of the new property.

>>>>

\usepackage{caption}
\usepackage{subcaption}
\usepackage[english]{babel}
\title{Spec2Fab: A  High-Fidelity Mapping from Specification to Fabrication}

@@

We will also use faster resonating actuators and high-speed
camera systems to track material deformations at high frame rates. Furthermore, we plan to track
the whole material volume rather than the outer material surface. This is possible since we can
print materials in clear color as well. Thus small color-coded markers can be easily embedded into
the material structure. These markers can be tracked in 3D using a multi-camera system.
\subsection{Optimization for Fabrication}
Caustics, shadowpix, balloon
\section{System Description}
The software framework (shown in Figure~\ref{fig:framework}) is composed of 
a set of software
modules that can be easily modified or exchanged. The first component
of this framework is an output-device-independent description API
that allows the user to specify any physical object in terms of its physical
properties such as geometry, mechanical behaviors, and appearance. 
The framework will also provide physically-based
simulation tools that accurately predict the behavior of our output device.
The goal of the optimization module is to search through
the space of possible device outputs and deliver one that best matches the
desired model. In order to evaluate the quality of the match between the
simulation output and the desired model we need to develop appropriate
comparison metrics. Finally, a central component of our framework is
a reduction model which makes the optimization problem tractable by
reducing the search space as much as possible.
The reduction model can specified by experts or deduced from a
set of examples. Next, we will describe each element of the framework in
more detail.
\begin{figure}
\includegraphics[width=0.45\textwidth]{figure/framework.pdf}
\caption{API overview. The diagram will become nicer.}
\label{fig:framework}
\end{figure}
\subsection{Input API}
Our input API handles three tasks: specifying an optimization problem,
maintaining a material library and configuring existing modules of
the optimization process.
An overview of the three components of our API is shown in Figure~\ref{fig:inputAPI}

\begin{figure}
\includegraphics[width=0.45\textwidth]{figure/inputAPI.pdf}
\caption{Input API. The diagram will become nicer.}
\label{fig:inputAPI}
\end{figure}

Our input API allows a designer to either
define material properties for sections of an object
or specify behavior of an object.
The designer
can use functions to describe properties such as reflectance (e.g., BRDFs, BSSRDFs), 
stiffness, or other spatially varying properties. 
Although it is possible to define the object directly by only specifying material
properties, intuitive user
interfaces will aid in specifying the objects and their properties
in terms of intuitive metaphors.
For example, the elastic properties of an object can be specified by a set of
example displacements from the rest pose and the corresponding applied forces.
\subsection{Search Space Decomposition and Reduction}
Our framework includes an optimization component that
searches through the space of possible device inputs
to find the one that best reproduces
the desired object. Unfortunately, this search space
is usually intractable. For example, when the printing
volume has N voxels and each of these voxels can be
assigned to one of M base materials, the search space
contains $N^M$ choices. To overcome this problem, we decompose the search
space into similar subproblems and also reduce
the search space to a lower-dimensional space using
a reduction model. The goal of the reduction step is to
shrink the search space as much as possible but at the
same time not to prune out good solutions. The low-dimensional space produced by the
reducer can be defined in two different ways. First, a reduction model can be explicitly specified by an expert, for
example, by defining structures of base materials and rules how different base materials can be combined together.
In this paper, all reduction models are manually specified by us.
The second way to specify a reduction model is implicit. In this case, the user provides a set of examples of
valid material structures. Then, a machine learning algorithm infers both basic material structures and the rules
for combining them. The optimization framework can be further improved by employing techniques that cluster
partial solutions that yield similar output properties, avoiding combinatorial explosion of the search space.
Furthermore, we can employ bounds on the solution based on physical constraints of the base materials.
\subsection{Optimization}
Our optimization component is an interface to
existing standard optimization techniques
such as simulated annealing, variational inference and
Markov Chain Monte Carlo methods,
as well as custom optimization algorithms implemented
by more advanced users.
\subsection{Simulation}
Another key step in the process of converting abstractions to physical output is being able to
simulate what an output device is going to generate given a well-defined input. 
A simulation allows the user to preview how the output will look and behave. 
This simulation is a generalization of the print-preview function
available in word processing applications.
As physical output generation might be costly or time-consuming, 
it is extremely beneficial for users to be able to preview the output and make immediate changes to the design.
That means that the simulation must accurately predict the output. 
It's necessary to develop very efficient and accurate rendering
and finite element simulation packages. Since we run the simulation multiple times within the optimization method
we can cache and reuse partial simulation results, speeding up the evaluation process at least 10-100 times.
Furthermore, we will ensure that the simulation is accurate by measuring properties of the printing materials and using
these measurements to estimate the parameters of data-driven material models (e.g., for elasticity, reflectance).

\section{Built-in Components}
We provide a built-in library that handles common tasks such as assigning texture,
simulating deformation, and optimizing for a stacking.
\subsection{Generator}
\begin{enumerate}
\item A generator that uses a uniform grids with homogeneous
material in each grid cell. (A foam structure is treated as one homogeneous material).
\item A generator that decomposes a mesh into columns of stackings where each
column can be addressed separately by Generator::chooseSection.
This is useful for problems where local changes don't global effects such as
matching texture, matching mechanical properties of each column.
\item A polynomial spline representation for modifying the surface mesh.
\item A polynomial spline for height field of internal material layers (does not modify
surface mesh).
\end{enumerate}

\subsection{Simulator}
\begin{enumerate}
\item Physics simulator with FEM, rigid body simulation
and simple collision resolution.
\item nVidia optiX to do photon mapping for caustics. Maybe also BRDF and shadows.
We need to look at its speed.
\item local computations such as reflectance and local mechanical properties given a stacking.
\end{enumerate}

\subsection{Metric}
Optionally returns a gradient represented as an array of signed floats.
\begin{enumerate}
\item Compare a mesh and its deformed state. There is one-to-one correspondence of 
vertices.
\item compare two images
\item compare two real numbers such as weight and bouncing height.
\end{enumerate}

\subsection{Optimizer}
\begin{enumerate}
\item MCMC, Simulated Anealing, SPSA
\item Branch and bound (plus clustering of similar configurations)
\item (Optional) reinforcement learning, deep neural networks...
\end{enumerate}

\section{Programming with Our API}
A casual user mostly make function calls to an existing 
manager to pass data and to run the optimization.
More advanced user can configure the manager to achieve more specific requirements.
For example, he can swap out an existing optimization module to achieve a better accuracy or 
a faster speed.
A professional user can implement more modules when he wants to deal with new
material properties that are not handled by our built-in library. In that case,
he needs to know what value the new property is in print materials, he needs to know
how to simulate for the new property, and how to measure error of the new property.
